---
title: "analysis"
author: "Ronit Dash"
format: html
execute:
  echo: false
---

```{r}
#| message: false
#| label: setup
library(tidyverse)
library(primer.data)
```
Subject: Longevity
Broad Question: Election Results and Lifespan

Specific question: How old will Preceptor live to be if he wins the election for mayor of Newton?
Causal Model

Potential Outcome: death_age

Units: The units are each candidate for mayor.

Covariates: election_age

treatment(?): winning the election 

Validity: Validity might not hold because different states have generally different life expectancies. There also might be a problem depending on how different mayoral elections are from gubernatorial elections.

```{r}
governors |> filter(state == "Massachusetts", status == "Challenger", sex == "Female")
```

Justice

Population Table: 

Units: 


Stability: Life expectancy increases over time, so it changes how much winning affects age.

Representativeness: The data includes states that don't represent the population of Massachusetts, and it only lists elections for governor, so no specific city populations.

Unconfoundedness: Basically airtight, because election success is However, it is not completely random, as outside factors lead males to be elected more freqeuently.
